\documentclass[./main.tex]{subfiles}

\begin{document}

The design is thought to satisfy the requirements shown in the RASD. To clarify the motivations that led to the definitions of the components here are reported the links between requirements and components.

%G1

\begin{itemize}
\item
  \textbf{R1} When a picture is taken using SafeReports, a new violation
  record is generated.
    \subitem 
    %TODO need to specify also user, app, router...?
    \textbf{ReportManager} and \textbf{PictureManager} are interested in the process. In particular PictureManager sends the picture to the ReportManager, which embeds the image with the other violation data.
  	
\item
  \textbf{R2} When a new violation record is generated, the current
  position of the user is added to the report.\\
  \textbf{R3} When a new violation record is generated, the timestamp is
  added to the report.
  \subitem
    \textbf{ReportManager} ensures to get the position and the timestamp from the picture data, which is sent to this component together with the image from \textbf{PictureManager}.
  
\item
  \textbf{R4} When a new violation record is generated, the photo is
  scanned by an OCR software to automatically detect the plate.
    
   \subitem
      \textbf{PictureManager} interacts with the OCR software to get the reading of the license plate and sends the result to \textbf{ReportManager}.
  
\item
  \textbf{R5} If the OCR software fails in detecting the plate, the user
  is notified and asked to repeat the procedure.\\
  \textbf{R6} If the OCR software detects the plate, the user is asked
  to confirm the violation report.
  \subitem
    In case of failure in the interpretation of the picture, \textbf{ReportManager} deals with the exception. The messages between this component and the user flow through the \textbf{Router} and of course occur inside the \textbf{UserApplication} (the only means of communication between users and the system).
  
\item
  \textbf{R7} If the user confirms the violation report, it is sent to
  SafeStreets.\\
  \textbf{R8} SafeStreets stores the information about the violation
  only if there aren't equivalent events already stored.
   \subitem
   \textbf{DBMS} deals with the duplicated violations and eventually discards them. If it considers the violation valid and receives the approbation of the user through \textbf{ReportManager}, it stores the data.
  
\end{itemize}

%G2

\begin{itemize}
\item
  \textbf{R9} SafeAnalytics allows common users to get data about
  violations selecting zone, time and type of violation.
  \subitem	
	\textbf{UserApplication} is aware of the type of user who is interacting with the system (thanks to \textbf{UserManager}) and allows it to send (through the Router) just the allowed filters to the \textbf{QueryHandler}.
  
\item
  \textbf{R10} SafeAnalytics anonymizes information before sending it to
  common users.\\
%G3
  \textbf{R11} SafeAnalytics allows authorities to get all the information
  stored by SafeStreets.
  \subitem
    \textbf{QueryHandler} deals with the data received and filters it for the common user, while letting all the informations available for the authorities.

\end{itemize}

%G4
\begin{itemize}
\item
  \textbf{R12} SafeStreets must store data about accidents provided by
  the municipality when available.
  \subitem
    \textbf{InfoUpdater} manages the periodic update of the database adding the data acquired from Information.
    
\item
  \textbf{R13} SafeStreets must analyze collected data crossed with data
  from the municipality to identify possible interventions.
  \subitem
    \textbf{QueryManager} gets the suggestions related to the user's query from \textbf{DBMS}, in particular {Datawarehouse}.
    
\item
  \textbf{R14} SafeSuggestions allows municipality users to get
  suggestions provided by SafeStreets.
  \subitem
  	\textbf{UserApplication} is aware of the type of user and  allows municipality users to access SafeSuggestions' functionalities through \textbf{Router}. 
\end{itemize}

%G5

\begin{itemize}
\item
  \textbf{R15} When the users send a violation report, its integrity is
  checked. \\
  \textbf{R16} If the integrity check is not successful, the violation
  report is discarded.
  \subitem
    %TODO is the camera check enough? add other checks?
  
\item
  \textbf{R17} SafeStreets must forward every new stored violation
  report to MTS to generate traffic tickets.
  \subitem
    \textbf{MTSManager} receives the data about the new violations from \textbf{ReportManager} and forwards it to MTS
\end{itemize}

%G6

\begin{itemize}
\item
  \textbf{R18} When a new ticket is generated using MTS, ticket-related
  data are stored by SafeStreets.\\
  \textbf{R19} SafeStreets must build statistics from stored data about
  issued tickets.
  \subitem
    The link between \textbf{MTSManager} and \textbf{DBMS} shows that the ticket data are stored in the database. The statistics are built inside the Datawarehouse.

\item
  \textbf{R20} SafeTickets allows authorities to get information and
  statistics on issued tickets.
  \subitem
    Since the data about issued tickets is saved in the database, authorities can access it as they do for the violations data.
\end{itemize}

%Non functional
\begin{itemize}
\item
  The system must be able to serve a great number of users reporting a
  violation simultaneously.
  \subitem
  	The database exploits an OLTP policy, that allows to manage a large number of transactions (the concurrency is internally handled by the DBMS).
\item
  SafeAnalytics must be able to provide the data requested by both
  common users and authorities in less than 3 seconds, to provide the
  best experience.
  \subitem 
  	The data warehouse pre-processes the data according to an OLAP policy, in order to speed up the queries.
\item
  The data about accidents provided by the municipality must be checked
  for updates at least every 5 minutes, to provide reliable and always
  updated suggestions.
  \subitem
    This can be achieved by setting the correct time T to activate the loop described in the AccidentUpdater sequence diagram, triggering \textbf{InfoUpdater} as frequently as needed.
\end{itemize}

\end{document}